Data Cleaning

### 2023-03-08 modeling_data/GLOBI_bee_update_clean.Rmd
commenting out write_csv

---
title:          Data Cleaning
output:         html_document
participants:   N. Bachelder, A. Chen, Z. Fang, M. Rapaport, S. Solomon
date:           Feb 18, 2021
source:         https://www.globalbioticinteractions.org/about
---

@@

# Export to csv file
```{r}
readr::write_csv(interactions, "interactions-14dec2022.csv")
```

>>>>

---
title:          Data Cleaning
output:         html_document
participants:   N. Bachelder, A. Chen, Z. Fang, M. Rapaport, S. Solomon, C. Smith
date:           Feb 18, 2021
source:         https://www.globalbioticinteractions.org/about
---

@@

# Export to csv file
```{r}
# readr::write_csv(interactions, "interactions-14dec2022.csv")
```
